Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-01-29 bbbq_article.tex
EOD

Both TMH prediction tools struggle with selenocysteine,
the 21st amino acid incorporated in human proteins.
The human reference proteome used contains 30 selenoproteins.
TMHMM gives a clear error message, due to which we removed
these selenoproteins from the analysis.
How PureseqTM deals with selenocysteine is unclear,
as it gives no error, nor is it mentioned anywhere,
nor do the authors respond to emails.
We assume PureseqTM ignores these residues.
In either case, we think that the effect of the 30 selenoproteins
on a proteome of 20600 proteins is only minor.

>>>>

We have removed the 25 selenoproteins found in the human
reference proteome, as both prediction tools struggle with 
selenocysteine, the 21st amino acid incorporated in human proteins.
TMHMM gives a clear error message, forcing us to remove
these selenoproteins from the analysis.
How PureseqTM deals with selenocysteine is unclear,
as it gives no error, nor is it mentioned anywhere,
nor do the authors respond to emails. Due to this, we removed the
selenoproteins from our analysis.
Another bug in PureseqTM is that it does not predict the topology
of proteins that have less than three amino acids. 
The TRDD1_HUMAN protein, short for 'T cell receptor delta diversity 1',
is, however, two peptides long. We manually added the prediction
that both peptides reside in the cytosol.
